---
title: "Project1"
author: "Demydiuk Oleksii"
date: "16 11 2020"
output: html_document
---

```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

# Reproducible Research - Course Project 1

### Loading and preprocessing data
```{r}
unzip("repdata_data_activity.zip")
data <- read.csv("activity.csv")
```
### What is a mean total number of steps taken per day?
```{r}
library(tidyverse)
library(lubridate)
Sys.setlocale("LC_TIME", "English")
p <- data %>%
  group_by(date)%>%
  summarise(steps = sum(steps, na.rm = T))%>%
  ggplot(aes(x=steps)) + geom_histogram(fill="steelblue")
ggsave("plot1.png")
p

```

### Mean and Median number of steps per day
```{r}
mm <- data %>%
   group_by(date) %>%
  summarise(steps = sum(steps, na.rm = T))%>%
  ungroup()%>%
  summarise(mean = mean(steps),
            median = median(steps))
 
```
Mean is `r mm$mean`

Median is `r mm$median`

### What is the average daily activity pattern?

```{r}
daily_activity <- data %>%
  group_by(interval)%>%
  summarise(steps_average = mean(steps, na.rm = T))

max_int <- daily_activity$interval[daily_activity$steps_average == max(daily_activity$steps_average)]

p <- ggplot(daily_activity,aes(x=interval,y=steps_average)) + geom_line(color='steelblue')
ggsave("plot2.png")
p


```

`r max_int`th 5-minute interval contains the maximum average number of steps across all the days in the dataset


## Imputing missing values

```{r}
na_count <- sum(is.na(data))

rep_data <- data %>%
  group_by(interval)%>%
  mutate(steps_average = mean(steps, na.rm = T),
         steps = ifelse(is.na(steps) == T, steps_average, steps))%>%
  select(-steps_average)
  

```
There is `r na_count` missing values was in dataset!


### What is a mean total number of steps taken per day?
```{r}
library(tidyverse)
library(lubridate)
Sys.setlocale("LC_TIME", "English")
p<-rep_data %>%
  group_by(date)%>%
  summarise(steps = sum(steps, na.rm = T))%>%
  ggplot(aes(x=steps)) + geom_histogram(fill="steelblue")
ggsave("plot3.png")
p

```

### Mean and Median number of steps per day
```{r}
rmm <- rep_data %>%
   group_by(date) %>%
  summarise(steps = sum(steps, na.rm = T))%>%
  ungroup()%>%
  summarise(mean = mean(steps),
            median = median(steps))
 
```

Mean is `r rmm$mean`

Median is `r mm$median`


Of course total number of steps by day increase

### Are there differences in activity patterns between weekdays and weekends?

```{r}
p <- rep_data %>%
  mutate(week_day = weekdays(as.Date(date)),
        is_weekend = as.factor(ifelse((week_day %in% c("Saturday","Sunday")) == T, "weekend", "weekday")))%>%
  group_by(interval, is_weekend)%>%
  summarise(steps_average = mean(steps, na.rm = T))%>%
  ggplot(aes(x=interval,y=steps_average, color = is_weekend)) + geom_line() + facet_wrap(~is_weekend, ncol = 1, nrow = 2)
ggsave("plot4.png")
p


```